\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-20 paper.qmd
Added models from phate for five Gaussian data

After establishing the hexagonal grid with an appropriate number of bins, some hexagonal bins may have few or no data points within them (see @fig-rmlowdenshex (a)). To ensure comprehensive coverage of the NLDR data, it is necessary to select hexagonal bins with a considerable number of data points. This involves calculating the number of points within each hexagon. Then, the standard count is computed by dividing the number of points within each hexagon by the maximum number of points in the grid (see @eq-equationp2). Next, bins with a standard count less than a certain benchmark value are removed (see @fig-rmlowdenshex (b)). The following steps will help in determining a suitable value for removing low-density hexagons:

@@

<!--trimesh with phate-->
```{r}
gau3_scaled_obj <- gen_scaled_data(
  data = phate_data_gau)
phate_gau_scaled <- gau3_scaled_obj$scaled_nldr

## Compute hexbin parameters
num_bins_x_gau3 <- 250
lim1 <- gau3_scaled_obj$lim1
lim2 <- gau3_scaled_obj$lim2
r2_gau3 <- diff(lim2)/diff(lim1)

gau3_model <- fit_highd_model(
  training_data = training_data_gau,
  emb_df = phate_gau_scaled,
  bin1 = num_bins_x_gau3,
  r2 = r2_gau3,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE,
  col_start_highd = "x"
)

df_bin_centroids_gau3 <- gau3_model$df_bin_centroids
df_bin_gau3 <- gau3_model$df_bin

>>>>

Once setting up the hexagonal grid with an appropriate number of bins, some hexagonal bins may have few or no data points within them (see @fig-rmlowdenshex (a)). To ensure comprehensive coverage of the NLDR data, it is necessary to select hexagonal bins with a considerable number of data points. This involves calculating the number of points within each hexagon. Then, the standard count is computed by dividing the number of points within each hexagon by the maximum number of points in the grid (see @eq-equationp2). Next, bins with a standard count less than a certain benchmark value are removed (see @fig-rmlowdenshex (b)). The following steps will help in determining a suitable value for removing low-density hexagons:

@@

<!--trimesh with phate-->
```{r}
# gau3_scaled_obj <- gen_scaled_data(
#   data = phate_data_gau)
# phate_gau_scaled <- gau3_scaled_obj$scaled_nldr
# 
# ## Compute hexbin parameters
# num_bins_x_gau3 <- 250
# lim1 <- gau3_scaled_obj$lim1
# lim2 <- gau3_scaled_obj$lim2
# r2_gau3 <- diff(lim2)/diff(lim1)
# 
# gau3_model <- fit_highd_model(
#   training_data = training_data_gau,
#   emb_df = phate_gau_scaled,
#   bin1 = num_bins_x_gau3,
#   r2 = r2_gau3,
#   is_bin_centroid = TRUE,
#   is_rm_lwd_hex = FALSE,
#   col_start_highd = "x"
# )
# 
# df_bin_centroids_gau3 <- gau3_model$df_bin_centroids
# df_bin_gau3 <- gau3_model$df_bin

df_bin_centroids_gau3 <- read_rds("data/five_gau_clusters/df_bin_centroids_gau_phate.rds")
df_bin_gau3 <- read_rds("data/five_gau_clusters/df_bin_gau_phate.rds")

### 2024-05-20 paper.tex
Added models from phate for five Gaussian data

After establishing the hexagonal grid with an appropriate number of
bins, some hexagonal bins may have few or no data points within them
(see \textbf{?@fig-rmlowdenshex} (a)). To ensure comprehensive coverage
of the NLDR data, it is necessary to select hexagonal bins with a
considerable number of data points. This involves calculating the number
of points within each hexagon. Then, the standard count is computed by
dividing the number of points within each hexagon by the maximum number
of points in the grid (see \textbf{?@eq-equationp2}). Next, bins with a
standard count less than a certain benchmark value are removed (see
\textbf{?@fig-rmlowdenshex} (b)). The following steps will help in
determining a suitable value for removing low-density hexagons:

>>>>

Once setting up the hexagonal grid with an appropriate number of bins,
some hexagonal bins may have few or no data points within them (see
\textbf{?@fig-rmlowdenshex} (a)). To ensure comprehensive coverage of
the NLDR data, it is necessary to select hexagonal bins with a
considerable number of data points. This involves calculating the number
of points within each hexagon. Then, the standard count is computed by
dividing the number of points within each hexagon by the maximum number
of points in the grid (see \textbf{?@eq-equationp2}). Next, bins with a
standard count less than a certain benchmark value are removed (see
\textbf{?@fig-rmlowdenshex} (b)). The following steps will help in
determining a suitable value for removing low-density hexagons:
